### 2022-07-25 paper/akweury/document.tex
update an (Trignet-CNN)

\begin{sidewaysfigure}[th]
	\centering
	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
	\caption{The architecture of TriGNet}
	\label{fig:VIL-Net}
\end{sidewaysfigure}

\subsection{An3 Net}
The first branch (shown above) takes a light map introduced in \ref{sec:lightmap} as the input, the structure is the same as GCNN architecture except that the last two standard convolution layers, the skip connections are kept to connect the 3 down/up samplings. 
The second branch (shown below) takes image as the input, the structure is the same as the first branch other than the input image is 1 channel but not 3 channels. 
The third branch takes the 3D vertex map as the input. The structure is based on GCNN architecture. However, in order to merge the other two branches, the vertex branch equips 4 times fusions in the up sampling part. Specifically, the first fusion locates immediately after the last gconv layer of the last down sampling, the second fusion after the second gconv layer of first up sampling, the third fusion after the second gconv layer of second up sampling, the fourth fusion after the second gconv layer of the third up sampling. Each fusion follows by an interpolation layer, a gconv layer to reduce the channel back to 32, a skip connection concatenate layer and another gconv layer to reduce the channel back to 32. After the fourth fusion, a gconv layer used for channel reduction, 2 standard conv layer for output prediction.

>>>>

\begin{sidewaysfigure}[th]
	\centering
	\includegraphics[width=1\textwidth]{Figures/vil-net} % Research group name and department name
	\caption{The architecture of VIL-Net}
	\label{fig:VIL-Net}
\end{sidewaysfigure}

\subsection{TriG-Net}

Based on above implementations, we propose a light and image guided network called Vertex-Image-Light Network (VIL-Net). The structure is basically derived from GCNN model as mentioned in \ref{sec:gcnn}, which is shown in Figure 
\ref{fig:VIL-Net}.

The first branch (shown above) takes a light map introduced in \ref{sec:lightmap} as the input, the structure is the same as GCNN architecture except that the last two standard convolution layers, the skip connections are kept to connect the 3 down/up samplings. 
The second branch (shown below) takes image as the input, the structure is the same as the first branch other than the input image is 1 channel but not 3 channels. 
The third branch takes the 3D vertex map as the input. The structure is based on GCNN architecture. However, in order to merge the other two branches, the vertex branch equips 4 times fusions in the up sampling part. Specifically, the first fusion locates immediately after the last gconv layer of the last down sampling, the second fusion after the second gconv layer of first up sampling, the third fusion after the second gconv layer of second up sampling, the fourth fusion after the second gconv layer of the third up sampling. Each fusion follows by an interpolation layer, a gconv layer to reduce the channel back to 32, a skip connection concatenate layer and another gconv layer to reduce the channel back to 32. After the fourth fusion, a gconv layer used for channel reduction, 2 standard conv layer for output prediction.

\begin{sidewaysfigure}[th]
	\centering
	\includegraphics[width=1\textwidth]{Figures/trignet} % Research group name and department name
	\caption{The architecture of Trig-Net}
	\label{fig:VIL-Net}
\end{sidewaysfigure}
